Manuscript Figures

### 2021-03-25 src/manuscript_figures.Rmd
plot overall survival

# factors to use in the model
clin_factors <- c('age_at_initial_pathologic_diagnosis', 'gender', 'ajcc_pathologic_tumor_stage')
event <- 'PFI'
time <- 'PFI.time'

>>>>

# factors to use in the model
clin_factors <- c('age_at_initial_pathologic_diagnosis', 'gender', 'ajcc_pathologic_tumor_stage')
event <- 'OS'
time <- 'OS.time'
